Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-11-20 3_review-responses/V3_review_responses/Reviewer #1 Response.txt

Reviewer #1 Response

Thank you for your comments. I will enclose them in hyphens and respond below that section for each comment.

In summary, we agreed with all the comments and revised the manuscript to reflect those changes, as well as added to the reviewed literature in the process.

------------
1. Conceptualisation of satisfaction
How is satisfaction defined in this paper? Is satisfaction different from "perceived value"? Can a customer be satisfied with one aspect while dissatisfied with other aspect? If so, is the customer a satisfied or dissatisfied customer? Satisfaction is a well-researched topic in the hospitality and tourism field and marketing field. Conceptual discussion of satisfaction is necessary.
------------

In our study, we consider the definitions by Hunt (1975) that satisfaction is a realization of a customer's expectation, and posit that customers can have different expectations towards different aspects of a service.

We added more discussion on the conceptual definition of satisfaction for the purposes of our study in section "3.2 Customer satisfaction and dissatisfaction towards individual factors during hotel stay", as well as an actual statement of our definition.

We previously hinged on citing previous definitions and expanding on that, but we agree that it is necessary to state our explicit intentions when discussing satisfaction.

However, we do realize that not knowing the overall satisfaction of each individual customer is a limitation of our study, and thus we added a statement in section "8. Limitations and Future Work.".

------------
2. Conceptualisation of omotenashi (in comparison to hospitality)
What makes Japanese omotenashi different from hospitality in other countries or even in Japan? Do all service organisations in Japan provide omotenashi (high level of hospitality)? What are the factors of omotenashi that differentiate itself form hospitality? Do all hotels provide omotenashi? If omotenashi is used to describe Japanese hospitality and not all hotels provide omotenashi, I recommend the authors to remove omotenashi from research questions (or replace it with another term like hospitality).
------------

In our study, we considered the word Omotenashi to be a cultural aspect in Japan that permeates every business practice. However, we do not intend to measure this influence, or to consider that certain hotels offer more or less omotenashi than others. Rather, our study focuses on the results of that influence: service, staff behavior and hospitality. All of these factors are universal to every kind of hotel, so we removed the word Omotenashi from our research questions.

We'd like to note that when speaking in Japanese, there is no other word for hospitality rather than omotenashi, so in the sense that we wrote this paper in Japan, we didn't realize there could be a theoretical confusion in this aspect. There is no practical difference of omotenashi and hospitality in Japan in the eyes of our study, and the only difference from other countries, is that the culture in Japan has a strong practice of this hospitality in any service business.

------------
3. WEIRD sample
The authors argued that WEIRD sample is biased. I would like to know how the samples for this study are not from WEIRD sample. Similarly, the authors are expected to elaborate on how well their sample represent the population (all Chinese and Western hotel guests). If the authors cannot prove, I recommend the authors to delete the WEIRD sample section or not to have discussion about a biased sample from the manuscript. Instead, the authors may want to elaborate on the role of culture in expectation and evaluation. What makes Chinese customers value hard attributes more than soft ones? I believe the value of this research is in the comparison between Chinese and Western customers, rather than a biased (WEIRD) vs. unbiased sample.
------------

Our samples are not from the WEIRD sample simply because we include non-Western subjects in our sample. However, we agree that arguing for biased or unbiased deters from the main objective of our paper, and adds little value to our argument. Therefore we removed it as asked.

We discuss the role of culture in expectation and evaluation a bit more, as we will state in the following comment.

------------
4. Discussion
I feel the discussion section reads like another version of findings/results. I expect more fundamental/theoretical discussions, which are derived from findings/results. What is known about Chinese and Western cultures? How do these known cultural characteristics affect evaluation of service? Are there something similar and/or different between what we know about the culture and what this study found?
------------

A

=======================
Minor comments:

1. High level of hospitality (line 127)
It is recommended to avoid such adjective-noun phrase as "high level" in this manuscript. How is "high level" of hospitality defined? Unless it is objectively measured, such a phrase is subjective and hurts reliability and validity of the paper.
------------

We rephrased to avoid being subjective in this matter.

------------
2. Not much value added (lines 130 - 136).
I am not sure what message these statements try to deliver.
------------

We removed these and rewrote part of this section to better flow into the research questions.

------------
3. Japanese omotenashi factors (line 139)
Do Japanese omotenashi factors mean hard and soft attributes in Japanese hotels? If so, in what aspects are they (hard and soft attributes in Japanese hotels) different from hard and soft attributes in other countries?
------------

We changed this to "hospitality and service factors". The misconstruction here is that the word Omotenashi in the Japanese language includes both hospitality and service, so it was used as an abbreviation for these. We realized this is confusing for people that don't speak Japanese so we removed instances where this happens across the paper (not only in line 139).

------------
4. Different reaction to Japanese omotenashi factors (line 145)
How is a reaction defined in this study? Isn't it evaluation, which emphasises cognitive and affective aspects, whereas reaction emphasises a behavioral aspect? 
------------

We changed this to evaluation, as pointed out.

------------
5. Hotel lodging (line 147)
It does not sound right. "hotel stay" would be better.
------------

We changed this in the manuscript.

------------
6. Easily changeable if small investments (line 646)
Again, "easily" and "small" are subjective. How is small investment defined? Getting rid of cigarette smell from rooms (assuming it requires the rooms unoccupied for a long period of time) may cost them more than renovating an entire floor.
------------

We changed the definition of soft and hard attributes to be less subjective. Soft attributes are those that the management and staff can directly influence, such as service factors. hard attributes are those that relate to physical aspects of the hotel, such as facilities, location, infrastructure, environment, etc. Technically speaking, the categories stay the same, but the definition lends itself to be objective in this definition.

------------

Thank you for your commentary, we hope this revised version is to your liking.

### 2020-11-20 1_manuscript/itt-emotion.tex
Did most of the reviewers comments except the discussion

  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most tourist behavior studies were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the soft attributes a hotel can change or be more concerned with hard attributes that hotel management cannot change? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives. We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists. The latter were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industrialized, rich, and democratic) populations that are culturally biased for the western world \cite[][]{nielsen2017}. The term WEIRD was coined by \cite{henrich2010weirdest}, who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world. This bias, albeit without the acronym, was discussed earlier about social psychology by \cite{hogan1978biases}. \cite{guaratne2009} pointed this bias out in discussions of globalization. At the same time, \cite{nielsen2017} sampled papers on developmental psychology and statistically examined this bias. This western bias is pervasive in all kinds of social sciences, and tourism science is not an exception. For example, studies are easily performed in the language of the scientist doing surveys for the subjects. A great majority of tourist behavior in history analysis has been performed with Western subjects and was thought to be universal until recent years.

  Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations. This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners make for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges. We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction. We define hard attributes as difficult or impossible elements to change by hotel management without investing in infrastructure or real estate. In contrast, soft attributes are easily modifiable by improvements in management.

@@

  \subsection{Japanese hospitality: \textit{Omotenashi}}\label{theory_omotenashi}

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training. High standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.

    It stands to reason that this high level of hospitality would be a positive aspect that would be at the top of satisfaction for any customer. However, in Japan, every business has this high level of hospitality, in differing levels of success. A simple convenience shop around the corner could be more hospitable if hotel management falls behind. Businesses have to strive to be the most hospitable, as hotels cannot lag in this competition. Thus, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer. Customers can always achieve satisfaction from hospitality elsewhere, so hotels need to be competitive in their hospitality.

@@

    \begin{subrsq}
    \begin{rsq}
    \label{rsq:omotenashi}
    To what degree are Chinese and Western tourists satisfied with Japanese \textit{omotenashi} factors such as staff behavior or service?
    \end{rsq}

    However, Japanese hospitality comes from Japanese culture. Different cultures interacting with it could have a different reaction. While some might be impressed by it, some might consider other factors more important to their stay in a hotel. This point leads us to a derivative of the above research question:

    \begin{rsq}
    \label{rsq:omotenashi_both}
    Do Western and Chinese tourists have a different reaction to Japanese \textit{omotenashi} factors such as staff behavior or service?
    \end{rsq}
    \end{subrsq}

  \subsection{Customer satisfaction and dissatisfaction during hotel lodging}\label{theory_satisfaction}

@@

@@

    Previous research has also focused on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}. However, little focus is put on hard factors uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.

@@

    % Asians vs. Western behavior
    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, henrich2010weirdest, guaratne2009, hogan1978biases}.

    Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior. \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism. This increase resulted in several studies focusing on only the behavior of this subset of tourists. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce. One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities. Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty. In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.

    One thing to note with the above Asian vs. Western analyses is that they were performed before 2000. The current Chinese economy boom is making an increase in the influx of tourists. The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations. In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves.

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}. We then determined the most commonly used words that contribute to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC). We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews. We split the dataset in price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels. We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review. We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}. Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel. Soft attributes are those that hotel management can easily change those attributes without investing in infrastructure or real estate. Hard attributes are impossible or impractical to change.

@@

    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel. We define these by the feasibility with which hotel management might improve to satisfy the customer further. We define hard attributes as matters that would be impossible for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but of high investment and risk. On the other hand, soft attributes are attributes of the hotel that are easily changeable if small investments are made. For example, the hotel's services or the cleanliness of the rooms are soft attributes. Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.

    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review. If the word is describing unchangeable factors by the staff or management, we consider them hard. If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft. For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset. We counted the percentage of usage in each context. If it is not clear from the word or the pairing alone, we declare it undefined. Then, we added the counts of these words in each category. A single word with no pairing is always 100\% in the category it corresponds to. We add the partial percentages for each category when an adjective includes various contexts. The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}. We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}. For the English keywords, see Figure \ref{fig:hard_soft_en}.

@@

    Our research questions were about two things. In research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the service and \textit{omotenashi} hospitality in Japan, and how are they different in their perceptions in this matter. We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}. From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings. When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges. From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment. However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots. Nevertheless, the most complained about aspect is the price of the hotel. Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.

@@

    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions. Here we define hard attributes as impossible or impractical to change for the hotel management, such as the surroundings, view, or location convenience. On the other hand, soft attributes are those that the hotel could easily and practically change without many limitations, such as improving the hotel's services via training or hiring specialized staff. In our study, we find that Chinese tourists are mostly positively reacting more to the hotel's hard attributes. There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit it is more uniform in this instance. English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes. In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.

@@

    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database. The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them. Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges. The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Like Chinese customers, Western customers also seem to enjoy the included breakfasts when it comes to their satisfaction keyword pairings. However, the word does not appear directly in the top 10 list as in their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''. When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively. The word ``great'', which is also high in most price ranges, and the top keyword in the highest-priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location'', ``great view'' and ``great service'', if we include the counts from all the price ranges together. Japanese high standards in hospitality very likely influenced this result.

@@

  Below we explore the possible interactions with \textit{omotenashi}; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry. We also discuss the differences between the hotel's hard and soft attributes and how they contribute to the satisfaction of customers.

>>>>

  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most tourist behavior studies were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the soft attributes of a hotel like service or be more concerned with hard attributes like location and facilities? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives. We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists. The latter were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  However, a great majority of tourist behavior analysis has been performed with Western subjects and a gap in knowledge and discussion existed until the recent decades. Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations. This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners make for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges. We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction. We define hard attributes as relating to physicial aspects and environmental aspects, such as the facilities of the hotel, the location of the hotel, infrastructure and real estate nearby. In contrast, soft attributes are the non-physical attributes of the hotel related to services, staff or management.

@@

  \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training. High standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}. This is permeating into every kind of business with customer interaction in Japan, where a simple convenience shop could express all of these standards of hospitality and service, which aren't exclusive to hotels.

    It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer. However, in many cases, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.  In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly, but rather consider it as a cultural factor that influences all businesses in Japan and observe the customers evaluations regarding service and hospitality factors in general, which can be compared to other places and business practice in the world. In summary, our study considers the influence of the cultural aspect of \textit{omotenashi}, while only studying the evaluations of service, hospitality and staff behavior factors that are universal to all hotels in any country.

@@

    \begin{subrsq}
    \begin{rsq}
    \label{rsq:hospitality}
    To what degree are Chinese and Western tourists satisfied with Japanese hospitality factors such as staff behavior or service?
    \end{rsq}

    However, Japanese hospitality comes from Japanese culture. Different cultures interacting with it could have a different evaluation of it. While some might be impressed by it, some might consider other factors more important to their stay in a hotel. This point leads us to a derivative of the above research question:

    \begin{rsq}
    \label{rsq:hospitality_both}
    Do Western and Chinese tourists have a different evaluation of Japanese hospitality factors such as staff behavior or service?
    \end{rsq}
    \end{subrsq}

  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}

@@

    In this study, however, we study not overall customer satisfaction, but the satisfaction and dissatisfaction that stem from individual specific expectations, be they conscious or unconscious. For example, if a customer has a conscious  expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter. However if that same customer had a conscious expectation of a comfortable sleep but there were loud noises at night, that is a different aspect that they can be dissatisfied with, regardless of the satisfaction towards the bed. Then, the same customer might have packed their own toiletries, thinking that the amenities might not include those, and then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation. While this definition of satisfaction and our current method does not allow us to examine overall customer satisfaction, it will allow us to examine the factors that a hotel can revise individually, and how they are perceived by a population as a whole. In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different aspects of a service. In our study, therefore, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service. Dissatisfaction, on the other hand, is the emotional response to the lack of a realization, or an under-performance of these conscious or unconscious expectations towards specific aspects of a service.

@@

    Previous research has also focused more on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}. However, hard factors uncontrollable by the hotel staff can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.

@@

    % Asians vs. Western behavior
    In the past, social science and tourism studies focused greatly on Western tourist behavior in other countries. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior. Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism. This increase in research on Chinese tourist behavior resulted in several studies focusing on only the behavior of this subset of tourists. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies specifically comparing Chinese and Western tourists. One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities. Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty. In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.

    One thing to note with the above Asian vs. Western analyses is that they were performed before 2000, and that they are not Chinese specific, but study Asian people in general. Meanwhile, the current Chinese economy boom is making an increase in the influx of tourists of this nation. The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations. In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves, making the analysis unique in the exploring of their behavior in comparison with Western tourists, as well as studying them in the specific environment of high-level hospitality in Japan and observing hard factors that are not considered in most other studies.

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}. We then determined the most commonly used words that contribute to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC). We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews. We split the dataset in price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels. We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review. We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}. Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel. Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which are able to be changed by the staff or management. Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, the surroundings of the hotel, which are impossible to change directly by the staff alone.

@@

    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel. We define hard attributes as matters regarding physical or environmental aspects of the hotel, such as facilities, location, or infrastructure, that would be impractical for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but regarding investment in infrastructure. On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management. For example, the hotel's services or the cleanliness of the rooms are soft attributes. For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the physical structure of the hotel are also considered soft attributes. Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.

    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review. If the word is describing unchangeable physical factors by the staff or management, we consider them hard. If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft. For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset. We counted the percentage of usage in each context. If it is not clear from the word or the pairing alone, we declare it undefined. Then, we added the counts of these words in each category. A single word with no pairing is always 100\% in the category it corresponds to. We add the partial percentages for each category when an adjective includes various contexts. The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}. We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}. For the English keywords, see Figure \ref{fig:hard_soft_en}.

@@

    Our research questions were about two things. In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter. We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}. From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings. When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges. From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment. However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots. Nevertheless, the most complained about aspect is the price of the hotel. Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.

@@

    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions. Here we define hard attributes as those relating to physical, structural or environmental aspects of the hotel, which are often impossible or impractical to change directly by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience. On the other hand, soft attributes are those that the hotel staff and management could practically change directly, such as improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness. In our study, we find that Chinese tourists are mostly positively reacting more to the hotel's hard attributes. There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit it is more uniform in this instance. English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes. In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.

@@

    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database. The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them. Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges. The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Like Chinese customers, Western customers also seem to enjoy the included breakfasts when it comes to their satisfaction keyword pairings. However, the word does not appear directly in the top 10 list as in their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''. When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.

@@

  Below we explore the possible interactions with Japanese hospitality; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry. We also discuss the differences between the hotel's hard and soft attributes and how they contribute to the satisfaction of customers.

  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
